---
title: "FinalCode"
output: html_document
---

```{r}
require(mosaic)
#install.packages("moments")
library(moments)
#install.packages("TTR")
require(TTR)
#install.packages("condmixt")
require("condmixt")
#install.packages("copula")
require(copula)
mydata <- read.csv("Return_dataset.csv", header=TRUE,as.is = T)
TradingDays <- subset(mydata, Trades == 0)
```

##Generating Student's t Parameters for Stocks-Bonds, Stocks-RealEstate, Bonds-RealEstate
```{r}
set.seed(100)
#Stocks and Bonds
u <- pobs(as.matrix(cbind(TradingDays$Stocks,TradingDays$Bonds)))[,1]
v <- pobs(as.matrix(cbind(TradingDays$Stocks,TradingDays$Bonds)))[,2]
selectedCopula <- BiCopSelect(u,v,familyset=2) 
rho1<- -0.1886762 #correlation parameter
df1<- 7.243498 #degrees of freedom 

#Stocks and RealEstate
w <- pobs(as.matrix(cbind(TradingDays$Stocks,TradingDays$RealEstate)))[,1]
x <- pobs(as.matrix(cbind(TradingDays$Stocks,TradingDays$RealEstate)))[,2]
selectedCopula <- BiCopSelect(w,x,familyset=2) 
rho2<- 0.4768359 #correlation parameter
df2<- 10.93676 #degrees of freedom 

#Bonds and RealEstate
y <- pobs(as.matrix(cbind(TradingDays$Bonds,TradingDays$RealEstate)))[,1]
z <- pobs(as.matrix(cbind(TradingDays$Bonds,TradingDays$RealEstate)))[,2]
selectedCopula <- BiCopSelect(y,z,familyset=2) 
rho3<- -0.07588851 #correlation parameter
df3<- 14.13204 #degrees of freedom 
```

##Generating Gaussian Parameters for Stocks-Bonds, Stocks-RealEstate, Bonds-RealEstate
#*Note: We are using t with original rho and 100 degrees of freedom to model Gaussian copula 
```{r}
set.seed(100)
#Stocks and Bonds
u <- pobs(as.matrix(cbind(TradingDays$Stocks,TradingDays$Bonds)))[,1]
v <- pobs(as.matrix(cbind(TradingDays$Stocks,TradingDays$Bonds)))[,2]
rho4<- -0.1886762 #correlation parameter
df4<- 100 #degrees of freedom 

#Stocks and RealEstate
w <- pobs(as.matrix(cbind(TradingDays$Stocks,TradingDays$RealEstate)))[,1]
x <- pobs(as.matrix(cbind(TradingDays$Stocks,TradingDays$RealEstate)))[,2]
rho5<- 0.4768359 #correlation parameter
df5<- 100 #degrees of freedom 

#Bonds and RealEstate
y <- pobs(as.matrix(cbind(TradingDays$Bonds,TradingDays$RealEstate)))[,1]
z <- pobs(as.matrix(cbind(TradingDays$Bonds,TradingDays$RealEstate)))[,2]
rho6<- -0.07588851 #correlation parameter
df6<- 100 #degrees of freedom 
```

#Checking and Plotting correlations
```{r}
par(mfrow=c(1,3))
#Stocks and Bonds
attach(TradingDays)
plot(Stocks,Bonds,pch='.')
abline(lm(Bonds~Stocks),col='red',lwd=1)
cor(Stocks,Bonds,method='spearman')

#Stocks and RealEstate
plot(Stocks,RealEstate,pch='.')
abline(lm(RealEstate~Stocks),col='red',lwd=1)
cor(Stocks,RealEstate,method='spearman')

#Bonds and RealEstate 
plot(Bonds,RealEstate,pch='.')
abline(lm(RealEstate~Bonds),col='red',lwd=1)
cor(Bonds,RealEstate,method='spearman')
detach(TradingDays)
```

##Generating Perspective/Density plots 
```{r}
set.seed(100)
par(mfrow=c(1,2))
persp(tCopula(dim=2,rho1, df=df1),dCopula, main = "Student's(Stocks & Bonds)")
persp(tCopula(dim=2,rho1, df=100),dCopula, main = "Gaussian (Stocks & Bonds)")

persp(tCopula(dim=2,rho2, df=df2),dCopula, main = "Student's(Stocks & RealEstate)")
persp(tCopula(dim=2,rho2, df=100),dCopula, main = "Gaussian (Stocks & RealEstate)")

persp(tCopula(dim=2,rho3, df=df3),dCopula, main = "Student's(Bonds & RealEstate)")
persp(tCopula(dim=2,rho3, df=100),dCopula, main = "Gaussian (Bonds & RealEstate)")
```

##Generating Marginal Distirbutions Plots
```{r}
attach(TradingDays)
par(mfrow=c(1,3))
Stocks_mu <- mean(Stocks)
Stocks_sd <- sd(Stocks)
Bonds_mu <- mean(Bonds)
Bonds_sd <- sd(Bonds)
RealEstate_mu <- mean(RealEstate)
RealEstate_sd <- sd(RealEstate)

#Plotting Stocks Returns
hist(Stocks,breaks=80,main="",freq=F,density=30,col='cyan')
lines(seq(-0.5,0.5,0.01),dnorm(seq(-0.5,0.5,0.01),Stocks_mu,Stocks_sd),col='red',lwd=2)

#Plotting Bonds Returns
hist(Bonds,breaks=80,freq=F,main="",density=30,col='cyan')
lines(seq(-0.5,0.5,0.01),dnorm(seq(-0.5,0.5,0.01),Bonds_mu,Bonds_sd),col='red',lwd=2,main="Bonds")
legend('topleft',c('Normal'),col=c('red'),lwd=2,cex =0.70)

#Plotting RealEstate Returns
hist(RealEstate,breaks=80,density=30,main="",col='cyan',freq=F)
lines(seq(-0.5,0.5,0.01),dnorm(seq(-0.5,0.5,0.01),RealEstate_mu,RealEstate_sd),col='red',lwd=2,main="RealEstate")
```

##Generating Simulations and Overlay of Actual Returns
#Stocks and Bonds (Gaussian and Student's t)
```{r}
set.seed(100)
par(mfrow=c(1,2))
copula_dist <- mvdc(copula=tCopula(rho1,dim=2,df=100), margins=c("norm","norm"),paramMargins=list(list(mean=Stocks_mu, sd=Stocks_sd),list(mean=Bonds_mu, sd=Bonds_sd)))
sim <- rMvdc(5000, copula_dist) #simulated data
plot(Stocks,Bonds,main='Returns Gaussian',pch=19)
points(sim[,1],sim[,2],col='red',pch=16)
legend('bottomleft',c('Observed ⍴s,b = -0.189 , dfs,b = 100','Simulated'),col=c('black','red'),pch=c(19,16),cex=0.50)

copula_dist <- mvdc(copula=tCopula(rho1,dim=2,df=df1), margins=c("norm","norm"),paramMargins=list(list(mean=Stocks_mu, sd=Stocks_sd),list(mean=Bonds_mu, sd=Bonds_sd)))
sim <- rMvdc(5000, copula_dist) #simulated data
plot(Stocks,Bonds,main='Returns Students t',pch=19)
points(sim[,1],sim[,2],col='red',pch=16)
legend('bottomleft',c('Observed ⍴s,b = -0.189 , dfs,b = 7.24','Simulated'),col=c('black','red'),pch=c(19,16),cex=0.50)
```

#Stocks and RealEstate (Gaussian and Student's t)
```{r}
set.seed(100)
par(mfrow=c(1,2))
copula_dist <- mvdc(copula=tCopula(rho2,dim=2,df=100), margins=c("norm","norm"),paramMargins=list(list(mean=Stocks_mu, sd=Stocks_sd),list(mean=RealEstate_mu, sd=RealEstate_sd)))
sim <- rMvdc(5000, copula_dist) #simulated data
plot(Stocks,RealEstate,main='Returns Gaussian',pch=19)
points(sim[,1],sim[,2],col='red',pch=16)
legend('bottomleft',c('Observed ⍴s,r = 0.477 , dfs,r = 100','Simulated'),col=c('black','red'),pch=c(19,16),cex=0.50)

copula_dist <- mvdc(copula=tCopula(rho2,dim=2,df=df2), margins=c("norm","norm"),paramMargins=list(list(mean=Stocks_mu, sd=Stocks_sd),list(mean=RealEstate_mu, sd=RealEstate_sd)))
sim <- rMvdc(5000, copula_dist) #simulated data
plot(Stocks,RealEstate,main='Returns Students t',pch=19)
points(sim[,1],sim[,2],col='red',pch=16)
legend('bottomleft',c('Observed ⍴s,r = 0.477 , dfs,r = 10.9','Simulated'),col=c('black','red'),pch=c(19,16),cex=0.50)
```

#Bonds and RealEstate (Gaussian and Student's t)
```{r}
set.seed(100)
par(mfrow=c(1,2))
copula_dist <- mvdc(copula=tCopula(rho3,dim=2,df=100), margins=c("norm","norm"),paramMargins=list(list(mean=Bonds_mu, sd=Bonds_sd),list(mean=RealEstate_mu, sd=RealEstate_sd)))
sim <- rMvdc(5000, copula_dist) #simulated data
plot(Bonds,RealEstate,main='Returns Gaussian',pch=19)
points(sim[,1],sim[,2],col='red',pch=16)
legend('bottomleft',c('Observed ⍴b,r = -0.0759 , dfb,r = 100','Simulated'),col=c('black','red'),pch=c(19,16),cex=0.50)

copula_dist <- mvdc(copula=tCopula(rho3,dim=2,df=df3), margins=c("norm","norm"),paramMargins=list(list(mean=Bonds_mu, sd=Bonds_sd),list(mean=RealEstate_mu, sd=RealEstate_sd)))
sim <- rMvdc(5000, copula_dist) #simulated data
plot(Bonds,RealEstate,main='Returns Students t',pch=19)
points(sim[,1],sim[,2],col='red',pch=16)
legend('bottomleft',c('Observed ⍴b,r = -0.0759 , dfb,r = 14.1','Simulated'),col=c('black','red'),pch=c(19,16),cex=0.50)
detach(TradingDays)
```
